\\Large The heat is on: Rising temperatures alter when, how, and where large terrestrial mammals move

### 2025-06-12 writing/manuscript.Rmd
added comments for local distance map

\noindent Species varied in both the direction and magnitude of predicted change in distance traveled, but worse climate-change scenarios always corresponded to greater absolute changes in behaviour (Figs. \@ref(fig:t-dist), B9, and B10). Under the best-case scenario, absolute changes by 2100 were small (approximately 0% to 4%), while under the worst-case scenario absolute changes ranged from ~2% (grizzly bear) to ~25% (cougars). However, while the models estimated that grizzly bears would move substantially less (if at all) in winter (Figs. \@ref(fig:dist), B4-B6), the models did not explicitly account for changes in hibernation phenology. Consequently, the climate change projections do not explicitly account for changes in energetic needs or physiology. Throughout BC (Fig. \@ref(fig:s-dist)), all species showed little to no absolute change under the best-case scenario (approximately 0-4% relative to 2025, on average), and approximately 2-25% average absolute change under the worst-case scenario, but the predicted changes varied spatially due to heterogeneity in climate change. Again, absolute changes were smallest under the best-case scenario and greatest under the worst-case scenario for all species.

@@

```{r s-dist, fig.cap="\\textbf{Climate change will impact each species' movement rates differently.} The color scale indicates the predicted changes in distance traveled in 2100, relative to each location's average distance in 2025 across all four scenarios, such that 1 indicates no change, values < 1 indicate a decrease, and values > 1 indicate an increase. For ease of readability, the color bar is on the $\\log_2$ scale to help visualize patterns in doubling, and values are capped to 0.67 and 1.5 ($\\approx 2^{\\pm 0.585}$; original data ranged 0.72 to 1.29). The predictions only account for the predicted temperature throughout the province and ignore environmental factors such as terrain slope, soil type, and forest cover."}
knitr::include_graphics('../figures/bc-displ-2100.png')
```

@@

```{r s-hrsfs, fig.cap="\\textbf{Climate change will impact each species' habitat relative selection strength (RSS) differently.} The color scale indicates the predicted changes in RSS in 2100, relative to each location's average RSS in 2025 across all four scenarios, such that 1 indicates no change, values < 1 indicate a decrease, and values > 1 indicate an increase. For ease of readability, the color bar is on the $\\log_2$ scale to help visualize patterns in doubling, and values are capped to 0.67 and 1.5 ($\\approx 2^{\\pm 0.585}$; original data ranged 0.26 to 117). The increase in boreal caribou's RSS for high elevations at warmer temperatures was highly uncertain and often not credible at the 95\\% level."}
knitr::include_graphics('../figures/bc-rss-2100.png')
```

>>>>

\noindent Species varied in both the direction and magnitude of predicted change in distance traveled, but worse climate-change scenarios always corresponded to greater absolute changes in behaviour (Figs. \@ref(fig:t-dist), B9, and B10). Under the best-case scenario, absolute changes by 2100 were small (approximately 0% to 4%), while under the worst-case scenario absolute changes ranged from ~2% (grizzly bear) to ~25% (cougars). However, while the models estimated that grizzly bears would move substantially less (if at all) in winter (Figs. \@ref(fig:dist), B4-B6), the models did not explicitly account for changes in hibernation phenology. Consequently, the climate change projections do not explicitly account for changes in energetic needs or physiology. Projected changes also varied spatially due to heterogeneity in projected climate change (Fig. \@ref(fig:s-dist)). Again, absolute changes were generally greatest under worse scenarios, but the direction of change at each location also varied across scenarios (most visible in cougars).

@@

```{r s-dist, fig.cap="\\textbf{Climate change will impact each species' movement rates differently.} The color scale indicates the predicted changes in distance traveled in 2100, relative to each pixel's average distance in 2025 across all four scenarios, such that 1 indicates no change, values < 1 indicate a decrease, and values > 1 indicate an increase. For ease of readability, the color bar is on the $\\log_2$ scale to help visualize patterns in doubling, and values are capped to 0.67 and 1.5 ($\\approx 2^{\\pm 0.585}$; original data ranged 0.50 to 1.56). The predictions only account for the predicted temperature throughout the province and ignore environmental factors such as terrain slope, soil type, and forest density."}
knitr::include_graphics('../figures/local-distance-2100.png')
```

@@

```{r s-hrsfs, fig.cap="\\textbf{Climate change will impact each species' habitat relative selection strength (RSS) differently.} The color scale indicates the predicted changes in RSS in 2100, relative to each location's average RSS in 2025 across all four scenarios, such that 1 indicates no change, values < 1 indicate a decrease, and values > 1 indicate an increase. For ease of readability, the color bar is on the $\\log_2$ scale to help visualize patterns in doubling, and values are capped to 0.67 and 1.5 ($\\approx 2^{\\pm 0.585}$; original data ranged 0.26 to 117). The increase in boreal caribou's RSS for high elevations at warmer temperatures was highly uncertain and often not credible at the 95\\% level."}
knitr::include_graphics('../figures/local-rss-2100.png')
```
